Comparing vector-based and Bayesian memory models using large-scale datasets:\protect\\User-generated hashtag and tag prediction on Twitter and StackOverflow

### 2015-05-28 writeups/psycMethods/psycMethods.tex
foo

22 different values of the decay rate parameter were explored
(0, .1, .2, .3, .4, .5, .6, .7, .8, .9, 1.0, 1.1, 1.2, 1.3, 1.4, 1.5, 1.6, 1.8, 2, 5, 10, 20).
The values were chosen to look at how performance changes from a pure frequency model ($d=0$), to a blend of frequency and recency ($d \approx .5$), to a pure recency model ($d=20$).
The decay rate value was varied for both the standard form and optimized learning form of $B_{i}$. 
Only values equal to or below 1 were examined for the optimized learning form, since values above 1 for this form cause a bifurcation and are not psychologically interesting.
The bifurcation occurs because at a decay rate of 1 the denominator of the first term to compute $B_{i}$ goes to zero (see Table \ref{tabACTRBLLModel}).

>>>>

22 different values of the decay rate parameter were explored
(0, .1, .2, .3, .4, .5, .6, .7, .8, .9, 1.0, 1.1, 1.2, 1.3, 1.4, 1.5, 1.6, 1.8, 2, 5, 10, 20).
The values were chosen to look at how performance changes from a pure frequency model ($d=0$), to a blend of frequency and recency ($d \approx .5$), to a pure recency model ($d=20$).
The decay rate value was varied for both the standard form and optimized learning form of $B_{i}$. 
Only values below 1 were examined for the optimized learning form, since values above 1 for this form are not mathematically defined. 
They are not mathematically defined at a decay rate greater than 1 because for these values the first term to compute $B_{i}$ is the logarithm of a negative number (see Table \ref{tabACTRBLLModel}).
At a decay rate equal to 1, every base-level activation $B_{i}$ is infinite, which is not psychologically interesting.
